### 2010-04-05 docs/architecture/architecture.tex
no longer need to set pmask
more on the initial models

   Note: for periodic boundaries, one must also set the corresponding
   {\tt pmask\_}\{{\em x,y,z}\} parameter.

\item {\tt pmask\_x }, {\tt pmask\_y }, {\tt pmask\_z } is set to 
   true ({\tt T}) to indicate that the boundary is periodic in the
   $x$, $y$, or $z$ coordinate directions.

@@

The routines in {\tt MAESTRO/initial\_model/} take a 1-d initial
model and map it onto a uniform grid, at the desired resolution, using
the equation of state in MAESTRO, and using MAESTRO's discretization of
hydrostatic equilibrium:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}

>>>>

@@

The routines in {\tt MAESTRO/initial\_model/} prepare an initial model
for MAESTRO.  There are two types of routines here, the first type
take an existing 1-d initial model produced somewhere else (e.g.\ a
1-d stellar evolution code), and and map it onto a uniform grid, at
the desired resolution, using the equation of state in MAESTRO, and
using MAESTRO's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}

The {\tt toy\_atm} example provides a simple approximation for a thin
(plane-parallel) convectively-unstable accreted layer on the surface
of a star.  This can be used as the starting point for a more complex
model.  Further details on the initial model routines can be 
found in \S~\ref{sec:initial_models_main}.
